---
title: "Project_1"
author: "Morgan Pena"
date: "2022-10-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Library and reading in data,message=FALSE}
library(tidyverse)
library(table1)

df <- read_csv('../DataRaw/lead-iq-01.csv')
```

```{r }
boxplot(IQ~Smelter,data=df, main="Children's IQ Levels by Smelter Location Status",
   xlab="Distence From Smelter", ylab="IQ Levels")
table1(~ IQ | Smelter, data = df)
```

This bar graph shows the average IQ levels of kids that are with in one mile of
the lead-emitting ore smelter "near" or more then one mile away from lead-emitting 
ore smelter "far'. The table is showing the mean and standard deviation of IQ 
scores for children near and far from smelter as well as medium, maxiumum and
minimum IQ scores for each group.

```{r, include=FALSE}
near <- df %>% filter(Smelter == "Near")
far <- df %>% filter(Smelter == "Far")

near.mean <- round(mean(near$IQ),2)
far.mean <- round(mean(far$IQ),2)
```

The mean IQ level for children within one mile of the smelters is `r near.mean` 
and the average IQ level for children outside of one mile of the smelters is `r far.mean`.